An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
config: small fix in intro
some grammar

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
that about 31\% system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
Misconfigurations, in practice, may result in various
system-wide problems, such as security vulnerabilities, 
application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

@@

To overcome these obstacles, researchers have proposed approaches based on
a statistical analysis and learning%
~\cite{wang04automatic, zhang14encore, yuan11context}
that try to infer the rules and policies 
how configuration files are constructed.
Rather than explicitly specifying entries' types or rules, 
these efforts are focused on learning policies from a sample dataset.
The learned rules are usually constructed along the following way: 
for every entry in a configuration file, 
they check if it deviates from a ``typical'' value, \ie, 
a value computed from a large training set 
consisting of configuration files.
If the entry is significantly different that the typical value, 
they suspect that it could be a potential configuration error.

@@

For practical purposes we use the dataset given at~\cite{configdataset}. Every file in our dataset contains an error, but it is 
always a different error and it only appears in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
way of deriving  
a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
rules we can efficiently check the correctness of the configuration files
of interest and detect potential errors.

>>>>

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
Misconfigurations, in practice, may result in various
system-wide problems, such as security vulnerabilities, 
application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

@@

To overcome these obstacles, researchers have proposed approaches based on
a statistical analysis and learning%
~\cite{wang04automatic, zhang14encore, yuan11context}
that try to infer the rules and policies 
how configuration files are constructed.
Rather than explicitly specifying entries' types or rules, 
these efforts are focused on learning policies from a sample dataset.
The learned rules are usually constructed in the following way: 
for every entry in a configuration file, 
they check if it deviates from a ``typical'' value, \ie, 
a value computed from a large training set 
consisting of configuration files.
If the entry is significantly different from a typical value, 
they suspect that it could be a potential configuration error.

@@

For practical purposes we use the dataset given at~\cite{configdataset}. 
Every file in our dataset contains several errors, 
but they are typically different errors and only appear 
in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
way of deriving  
a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
rules we can efficiently check the correctness of the configuration files
of interest and detect potential errors.
